SPARQL on the open, decentralised Web

### 2016-06-05 dissertation/related.tex
Cache problems and solutions
improve Attean on HERMES a note

\subsection{Query answering with cache}

First, we note some claims that SPARQL query caching is not possible:
In \cite{hogan2014paths}, the authors examine cacheable as one of the
desiderata for sustainable data access. They claim, without further
justification, that SPARQL isn't cacheable. With this work and much of
the below related work, I suggest they are mistaken. Not only can
whole SPARQL queries be cached, but it is possible to break down the
query to parts that can be cached.

@@

HERMES \cite{adali1996query} provided motivation for
\ref{sec:conpush}, but is also important prior art for the work in
Chapter~\ref{sec:tpfcacheplanning}. An important concept in the HERMES
system is ``invariants''. They are, in our terminology, patterns that
do not need to be looked up remotely, but can be integrated in the
query answer by the mediator. The expectation in HERMES is that such
invariants will be encoded by a domain expert. The Attean framework
provides facilities to do so by using traits. Attean can also pass the
task of computing a scalar cost metric by a similar mechanism, but
HERMES has a more advanced cost model in that it has a cost vector
with estimates for time required to find the first answer, time to
find all answers and the cardinality of the answer set. Caching
summary statistics is another important feature of HERMES, and it also
contributes lossy and lossless summaries, for the purpose of saving
space and reduce the time it takes to compute a cost estimate. HERMES
further has a query rewriter and optimiser, that rewrites the query
taking into account the cache and the invariants. While HERMES is more
general than what I detail in Chapter~\ref{sec:tpfcacheplanning}, we
note that while invariants could be coded in Attean, a SPARQL query
cache should be oblivious to domain knowledge and therefore shouldn't
assume any invariants, except in the possible but unlikely case where
the remote server declares that an infinite freshness lifetime for the
result of a certain graph pattern. While statistics summarisation is
relevant and should be studied in future work, we note that with a
Linked Data Fragments server, a cardinality estimate is required to be
available for every triple pattern, and is also cacheable with the
same constraints as the data themselves.

>>>>

\subsection{Query answering with cache}\label{sec:relcache}

First, we note a claim that SPARQL query caching is not possible:
In \cite{hogan2014paths}, the authors examine cacheable as one of the
desiderata for sustainable data access. They claim, without further
justification, that SPARQL isn't cacheable. With this work and much of
the below related work, I suggest they are mistaken. Not only can
whole SPARQL queries be cached, but it is possible to break down the
query to parts that can be cached.

@@

HERMES \cite{adali1996query} provided motivation for
\ref{sec:conpush}, but is also important prior art for the work in
Chapter~\ref{sec:tpfcacheplanning}. An important concept in the HERMES
system is ``invariants''. They are, in our terminology, patterns that
do not need to be looked up remotely, but can be integrated in the
query answer by the mediator. The expectation in HERMES is that such
invariants will be encoded by a domain expert. The Attean framework,
which is used extensively in this work and is detailed in Section~\ref{sec:attean}
provides facilities to do this in an easy and extensible way, and also
accommodates for the task of computing a scalar cost metric, but
HERMES has a more advanced cost model in that it has a cost vector
with estimates for time required to find the first answer, time to
find all answers and the cardinality of the answer set. Caching
summary statistics is another important feature of HERMES, and it also
contributes lossy and lossless summaries, for the purpose of saving
space and reduce the time it takes to compute a cost estimate. HERMES
further has a query rewriter and optimiser, that rewrites the query
taking into account the cache and the invariants. While HERMES is more
general than what I detail in Chapter~\ref{sec:tpfcacheplanning}, we
note that while invariants could be coded in Attean, a SPARQL query
cache should be oblivious to domain knowledge and therefore shouldn't
assume any invariants, except in the possible but unlikely case where
the remote server declares that an infinite freshness lifetime for the
result of a certain graph pattern. While statistics summarisation is
relevant and should be studied in future work, we note that with a
Linked Data Fragments server, a cardinality estimate is required to be
available for every triple pattern, and is also cacheable with the
same constraints as the data themselves.
